Comment: Reasoning about Interference Between Units

### 2016-03-26 paper/introduction.tex
Fixing caption for Figure 2

\begin{figure}[H]\centering
  \includegraphics[width=.9\textwidth]{ksvsssr-boxplots.pdf}
  \caption{Distributions of the simulated data from left to right: $y_0$
    outcome with no experiment, observed outcome after random assignment,
    outcomes implied by a constant additive model of effects ("Add. Model"), outcomes implied by a constant
    multiplicative model ("Mult. Model"). The hypothesized model parameters $\tau_0$ that
    produce the patterns shown are printed on the plot. The proportion of
    simulated tests in which these values of $\tau_0$ with $p$-values less
    than $\alpha=.05$ by the KS and SSR test statistics are printed on the plot as $\text{pow}_{KS}$ and
  $\text{pow}_\text{SSR}$. The SSR test statistic has more power for the
  Normal outcomes and less power for the skewed outcome.}\label{fig:boxplot}
\end{figure}

>>>>

\begin{figure}[H]\centering
  \includegraphics[width=.99\textwidth]{ksvsssr-boxplots.pdf}
  \caption{The SSR test statistic has more power than the KS test statistic for the Normal outcome and
    less power for the skewed outcome. Each panel shows distributions of simulated data from left to right:
    outcome with no experiment ($y_0$), observed outcome after random assignment,
    outcomes implied by a constant additive model of effects (``Add. Model''),
    and outcomes implied by a constant multiplicative model (``Mult. Model''). The hypothesized model parameters $\tau_0$ that
    produce the patterns, and the power of the tests using the KS and SSR test
    statistics, are printed below the models.}\label{fig:boxplot}
\end{figure}
